% Resume
% ATS-Friendly Resume in LaTeX (1 Page Refined)
% Mohamed Muaath Rifath
% End preamble

\documentclass[10pt, letterpaper]{article}

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[empty]{fullpage}
\usepackage[margin=0.3in, top=0.25in, bottom=0.2in]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{xcolor}
\usepackage[colorlinks=true, urlcolor={blue!70!black}, linkcolor=black]{hyperref}

% Keep text justified while avoiding end-of-line word breaks.
\hyphenpenalty=10000
\exhyphenpenalty=10000
\sloppy

% Remove page numbers
\pagestyle{empty}

% Section formatting
\titleformat{\section}{\normalsize\bfseries\uppercase}{}{0em}{}[\titlerule]
\titlespacing*{\section}{0pt}{1pt}{1pt}

% Compact lists
\setlist[itemize]{nosep, leftmargin=12pt, topsep=1pt, partopsep=0pt, parsep=0pt, itemsep=1pt}

% Custom commands
\newcommand{\resumeEntry}[4]{
  \noindent\textbf{#1} \hfill #3 \\[-2pt]
  \textit{#2} \hfill \textit{#4}
}

\newcommand{\resumeProject}[2]{
  \noindent\textbf{#1}\ {\small\textperiodcentered\ #2}
}

\begin{document}

% Header
\begin{center}
  {\Large\bfseries Mohamed Muaath Rifath} \\[2pt]
  {\large Software Engineer} \\[2pt]
  {\small \href{mailto:me@muaathrifath.me}{me@muaathrifath.me} \enspace{\large\textbullet}\enspace \href{tel:+918883735079}{+91 88837 35079} \enspace{\large\textbullet}\enspace Chennai, India} \\[1pt]
  {\small \href{https://muaathrifath.me}{muaathrifath.me} \enspace{\large\textbullet}\enspace \href{https://linkedin.com/in/muaath-rifath}{linkedin.com/in/muaath-rifath} \enspace{\large\textbullet}\enspace \href{https://github.com/muaath-rifath}{github.com/muaath-rifath}}
\end{center}

\vspace{-8pt}

% Professional Summary
\section{Professional Summary}
{\small Software Engineer focused on shipping zero-to-one products. I build systems across distributed Go backends, AI-integrated frontends, and custom ESP32 firmware. I prioritize reliability in core infrastructure like identity and payments, building with security and scalability in mind to support product growth. My focus is on solving the technical challenges of early-stage development to ensure a stable foundation for the product.}

\vspace{1pt}

% Experience
\section{Experience}
\resumeEntry{Introspect Labs}{Full Stack Developer}{Oct 2025 -- Feb 2026}{Remote, Bengaluru, India}
\begin{itemize}
  \item Architected the v1 backend for uyir.ai, migrating the identity layer from legacy OTP to Zitadel OIDC; implemented automatic JWT refresh and patched critical Next.js CVEs mid-deployment.
  \item Engineered a \textbf{reconnection-aware attendance tracking system} for LiveKit video sessions using \textbf{event-sourced audit logs} and idempotency guards to handle webhook race conditions and network drops.
  \item Built the full Next.js 15 frontend from scratch with custom Tiptap diff marks for inline AI editing, therapist dashboards, and a \textbf{presigned S3 upload workflow} for AI avatar training data.
  \item Containerized the stack with Docker, set up self-hosted GitHub Actions CI/CD with Nginx reverse proxy, and migrated from SMTP to AWS SES for scalable transactional emails.
  \item Optimized database performance via PostgreSQL schema design and Alembic migrations, supporting complex therapist-user scheduling and multi-tier subscription billing.
\end{itemize}

\vspace{1pt}

% Projects
\section{Projects}
\resumeProject{Sol, Open Distributed Smart Home \& Agentic Orchestration Platform}{Go 1.25, ESP32-S3, MQTT, LiveKit, MCP, TimescaleDB, MinIO, ZITADEL, mTLS}
\begin{itemize}
  \item Architected a 4-tier agentic platform featuring a Go control plane and ESP32-S3 nodes, validated through hardware deployment with per-device X.509 mTLS security.
  \item Engineered a \textbf{1.2s latency voice pipeline} using on-device wake-word detection (WakeNet9), LiveKit WebRTC streaming, and Azure OpenAI Realtime API for agentic reasoning.
  \item Hardened AI-to-hardware reliability via a \textbf{pgvector/HNSW grounding layer} that resolves natural language device references to UUIDs with sub-millisecond latency.
  \item Developed a zero-install \textbf{WebSerial provisioning flow} for browser-based firmware flashing and OIDC device-code registration, eliminating the need for local IDEs.
  \item Built a native MCP server with capability-based authorization, exposing a standard interface for \textbf{external agents (OpenClaw, NemoClaw, Claude)} to discover and actuate hardware.
\end{itemize}

\vspace{1pt}
\resumeProject{Zylert, LLM-Orchestrated Notification Triage System}{Kotlin, Android SDK 36, Room, Node.js, OpenAI/Mistral, Zod}
\begin{itemize}
  \item Architected an Android-to-Node.js pipeline that intercepts and triages push notifications in real time using \textbf{LLM-backed semantic classification}.
  \item Hardened LLM output reliability using \textbf{strict Zod validation} and fallbacks to handle malformed payloads and ensure 99\% parsing accuracy.
  \item Engineered a priority routing system that surfaces critical human messages while compressing low-value automated noise via conversational querying.
\end{itemize}

\vspace{1pt}
\resumeProject{Threble, Open-Source Social Network}{Next.js 15, TypeScript, NextAuth, Prisma, PostgreSQL, Redux/RTK, Azure Blob}
\begin{itemize}
  \item Developed an open-source social platform featuring a LinkedIn-style graph with connection requests, mutual-connection lookups, and community roles.
  \item Implemented route protection with NextAuth, Prisma/PostgreSQL persistence, and responsive UI with mobile-aware notification flows.
\end{itemize}

\vspace{1pt}

% Skills
\section{Skills}
\noindent\textbf{Languages:} TypeScript, Go, Python, Kotlin, C/C++ (ESP-IDF/Arduino), SQL, Shell/Bash, HTML/CSS \\
\textbf{Frontend/Mobile:} Next.js 16, React 19, D3.js, Three.js, R3F, Tailwind CSS, Zustand, Redux, Framer Motion, Android SDK \\
\textbf{Backend/DevOps:} FastAPI, Node.js, PostgreSQL (TimescaleDB/pgvector), MongoDB, Prisma, Celery, Redis, MQTT, Docker, Traefik, MinIO, GitHub Actions, AWS \\
\textbf{AI/Security:} OpenAI Realtime, LiveKit, RAG Pipelines, Zitadel OIDC, mTLS, X.509, OAuth 2.0, JWT, HMAC-SHA256

\vspace{1pt}

% Certifications
\section{Certifications}
\begin{itemize}
  \item \textbf{MCP: Build Rich-Context AI Apps with Anthropic} -- DeepLearning.AI (May 2025)
  \item \textbf{Docker Foundations Professional Certificate} -- Docker, Inc. (Feb 2026)
  \item \textbf{Foundation of Cloud IoT Edge ML} -- NPTEL (May 2024)
\end{itemize}

\vspace{1pt}

% Education
\section{Education}
\resumeEntry{Aalim Muhammed Salegh College of Engineering}{B.E. in Electronics \& Communication Engineering}{2022 - 2026}{Chennai, India}









\end{document}
